---
title: "Assignment 4 R - RStudio"
author: "Nabila Hossain"
date: "July 26, 2015"
output: 
  html_document: 
    keep_md: yes
---

Use base R graphics, or a graphics package of your choice. You should include at least one example of each of the following:
  + histogram
  + boxplot
  + scatterplot
Do the graphics provide insight into any relationships in the data?


```{r}
library(ggplot2)
summary(midwest)
```



__Does the population vary from state to state?__

```{r}
z <- rowsum(midwest$poptotal, midwest$state)
z
s <- ggplot(data = midwest, aes(x = state, y = poptotal, fill = state))
s + geom_histogram(stat="identity") + ggtitle("Midwest States Vs. Total Population") +
xlab("Midwest States") + ylab("Total Population")

```

Answer: Based on the histogram above we see that...........

__Does college education have effect on proverty?___

```{r}
p <- ggplot(data = midwest, aes(y = percpovertyknown, x = percollege))
p + geom_point((aes(color = state))) + ggtitle("College Education Vs Total Proverty") +
xlab("Percent College Educated") + ylab("Percentage of Total proverty")
p + geom_point(aes(color = state)) + facet_wrap(~state) + ggtitle("College Education Vs Total Proverty by Each Midwest State") +
xlab("Percent College Educated") + ylab("Percentage of Total proverty")

```

Answer: Based on the scatter plot above we see that...........

```{r}
A <- matrix(data=c(1,2,-3,2,1,-3,-1,2,0), nrow=3, ncol=3, byrow=TRUE)    

B <- matrix(data=c(5,13,-8), nrow=3, ncol=1, byrow=FALSE)

library(MASS)

fractions(solve(A, B), 3) 


```

